Formalization of Network Flow Algorithms

### 2017-03-03 paper/root.tex
More precise description of overflow bugs

  We implement capacities by (arbitrary precision) integer numbers\footnote{Up to this point, the formalization models capacities as \emph{linearly ordered integral domains}, which subsume reals, rationals, and integers. Thus, we could chose any executable number representation here.}. Note that an implementation by fixed precision numbers would also be possible,
  but requires additional checks on the network to ensure that no overflows can happen.\footnote{Actually, the unverified reference 
  implementations of the push-relabel algorithms~\cite{Gold_Network_Opt,ICPC-notebook} that we use in our benchmarks (\cf Section~\ref{sec:benchmark}) lack such checks, and silently report erroneous maximum flow values in case of overflow.}
  % TODO: Can we trick the Java reference implementation on integer overflow?
  Nodes are represented by natural numbers less than an upper bound $N$, and residual graphs are implemented by their capacity matrices, which, in turn,
  are realized as arrays of size $N\times N$ with row-major indexing, such that the successors of a node are close together in memory.
  The adjacency map of the network is implemented by an array of lists of nodes. 
  An augmenting path is represented by a list of edges, \ie a list of pairs of nodes. 
  The height frequency map and the maps from nodes to height labels and excess values are implemented by arrays.
  The queue of the FIFO push-relabel algorithm and the list of the relabel-to-front algorithm are implemented by two stacks, allowing for amortized constant time operations.

>>>>

  We implement capacities by (arbitrary precision) integer numbers\footnote{Up to this point, the formalization models capacities as \emph{linearly ordered integral domains}, which subsume reals, rationals, and integers. Thus, we could chose any executable number representation here.}. Note that an implementation by fixed precision numbers would also be possible,
  but requires additional checks on the network to ensure that no overflows can happen.\footnote{Actually, the unverified reference 
  implementations of the push-relabel algorithms~\cite{Gold_Network_Opt,ICPC-notebook} that we use in our benchmarks (\cf Section~\ref{sec:benchmark}) lack such checks, and silently report erroneous maximum flow values in case of overflow. One implementation~\cite{ICPC-notebook} has a parser that silently ignores overflows, 
  while the other~\cite{Gold_Network_Opt} uses a too small integer type for the excess flow.}
  % TODO: Can we trick the Java reference implementation on integer overflow?
  Nodes are represented by natural numbers less than an upper bound $N$, and residual graphs are implemented by their capacity matrices, which, in turn,
  are realized as arrays of size $N\times N$ with row-major indexing, such that the successors of a node are close together in memory.
  The adjacency map of the network is implemented by an array of lists of nodes. 
  An augmenting path is represented by a list of edges, \ie a list of pairs of nodes. 
  The height frequency map and the maps from nodes to height labels and excess values are implemented by arrays.
  The queue of the FIFO push-relabel algorithm and the list of the relabel-to-front algorithm are implemented by two stacks, allowing for amortized constant time operations.
